---
title: "Creating graphs with ggplot2"
author: "Jeremy Lang"
date: "1/27/2020"
output: html_document
---

# Plots with ggplot2

We are going to make plots in R using the ggplot2 package from the tidyverse.

```{r}

library(tidyverse)
library(readxl)
library(here)

```

# California National Parks Data

```{r}

ca_np <- read_csv(here("data", "ca_np.csv"))
ci_np <- read_excel(here("data", "ci_np.xlsx"))

```

## make my own first graph!

We're going to make a line plot of year (x-variable) vs vistiors (y variable) in ggplot:

```{r}

ggplot(data = ci_np, aes(x = year, y = visitors)) + 
  geom_line() +
  geom_point()

```

Make a base layer for my CI plots:

```{r}

gg_base <- ggplot(data = ci_np, aes(x = year, y = visitors))
gg_base + geom_point()

```

### Now let's start customizing!

- line / point colors: color
- change line type: linetype
- change point style: pch
- change transparency: alpha

```{r}

gg_np <- ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name))

gg_np +
  geom_line(show.legend = FALSE) +
  theme_light() + 
  labs(x = "year", y = "annual visitors") +
  facet_wrap(~ park_name)

ggsave(here("figures", "np_graph.jpg"), dpi = 180, width = 8, height = 7)

```





